{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-07-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, late night final additions

\chapter{Application, Linear Feasibility Problems}
    This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}.

@@

        We first introduce the linear feasibility problem as our primary problem. 
        \begin{definition}[a linear conic feasibility problem]\label{def:lcf-problem}
            Let $A\in \RR^{m\times n}$, $b \in \RR^{m\times p}$
            Let $\mathcal K \in \RR^{n \times p}$ nonempty, closed convex cone. 
            The conic feasibility problem is defined as the following optimization problem: 
                \min_{X \in \mathcal K} \Vert AX - B\Vert^2_F.
        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$ and $p = 1$ making $x \in \RR^{n}$. 
        A feasibility semidefinite program with linear constraint is another example. 

>>>>

\chapter{Application, Linear Feasibility Problems}
    This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}.
    We first introduce the linear feasibility problem as our primary problem. 
    \begin{definition}[a linear conic feasibility problem]\label{def:lcf-problem}
        Let $A\in \RR^{m\times n}$, $b \in \RR^{m\times p}$
        Let $\mathcal K \in \RR^{n \times p}$ nonempty, closed convex cone. 
        The conic feasibility problem is defined as the following optimization problem: 
        \begin{align*}
            \min_{X \in \mathcal K} \Vert AX - B\Vert^2_F.
        \end{align*}
    \end{definition}
    Next, we will give some examples of mathematical programming models that fit the above problem type. 
    \begin{definition}[semidefinite programming]\label{def:SPD}

    \end{definition}
    \begin{definition}[linear feasibility problen]\label{def:LSP}

@@
